---
title: "W_UP_01"
author: "Sasha Sanchez"
date: "Summer 2020"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
The boxplot for the skill players shows that they do a lot more pushups compared to the boxplot of the line players. The skill players boxplots 25th percentile is higher than the boxplot of line players 75th percentile.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Numerical results

```{r}
favstats(pushups~position,data=mydata)
```
The average number of pushups done by a line player is around 17. While the skill players have an average number of pushups around 50. 

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
The p-value is very low which means that we will reject null hypothesis. There is a difference when it comes to the amount of pushups line and skill players can preform. The skill players on average do three times the amount of pushups compared to the line players. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
First we did a variable analysis from which we looked at our variables given in order to help identify which helper file was needed. Then from looking at our variable we needed the numerical~cat helper file in order to help us with this problem. After loading up the numerical~cat helper file, I was able to copy and paste the commands after changing the variables within the command. From the results I concluded that I reject the null hypothesis. This means that there is a major difference in the amount of pushups a skill player can preform compared to a line player.     
